---
title: "COD Reproducibility Report"
output:
  html_document:
    toc: true
    toc_float: true
---

#### Article ID: Xvfpm
#### Pilot: Kyle MacDonald
#### Co-pilot: Tom Hardwicke  
#### Start date: 4/27/17
#### End date: [Insert end date - use US format]   

-------

#### Methods summary: 
[Write a brief summary of the methods underlying the target outcomes written in your own words]

------

#### Target outcomes: 

For this article you should focus on the findings reported in section 2.2.1. Specifically, you should attempt to reproduce all descriptive and inferential analyses reported in the text below and associated tables/figures:

> Starting with the dimension of corridor distance and its influence on pointing latency, we conducted an ANOVA with the between-participant factor environment (ES vs. VS) and the within-participant factor corridor distance. A main effect of corridor distance, F(3, 66) = 5.47, p = 0.008, ηp2 = 0.20, and an interaction of corridor distance × environment, F(3, 66) = 4.58, p = 0.017, ηp2 = 0.17, but no main effect of environment, F < 1, p > 0.800, were found. Thus, the influence of corridor distance on latency differed between environments. To further examine this interaction we regressed pointing latency onto corridor distance separately for each participant. From these regressions b was extracted. This standardized slope describes the linear change of latency with increasing corridor distance for every participant. Fig. 3, top left, depicts the individual and mean slopes for the two environmental conditions. T-tests were used to analyze slopes. As expected, slopes derived from ES did exceed 0, mean b = 0.22, t(11) = 8.15, p < 0.001, d = 2.35 (see Fig. 3, top right), indicating an increase in pointing latency the more corridors are residing between current and target location. With each additional corridor pointing took on average 1.02 s (SD = 0.53) longer. In VS, which worked as the control condition where no latency increase with ascending corridor distance was expected, the mean slope did not differ from 0, mean b = 0.02, t(11) = 0.63, p = 0.542, d = 0.18. Thus, pointing did not take longer the further away targets were located with respect to corridors. Additionally, a comparison of mean slopes between ES and VS revealed that the linear increase of latency across ascending corridor distance was higher for ES compared to VS, t(22) = −4.28, p < 0.001, ds = 1.75. This pattern was also evident in individual slopes. Whereas in ES data of each single participant rendered a positive slope, in VS this was only the case for 7 out of 12 participants. Results suggest that in ES memory, the spatio-temporal pattern of learning was preserved and this was not due to the structure of the layout itself.

------

```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, warning=FALSE, message=FALSE)
```

## Step 1: Load packages

```{r}
library(tidyverse) # for data munging
library(knitr) # for kable table formating
library(haven) # import and export 'SPSS', 'Stata' and 'SAS' Files
library(readxl) # import excel files
library(CODreports) # custom report functions
library(magrittr)
library(stringr)
```

## Step 2: Load data

```{r}
```

## Step 3: Tidy data

```{r}
```

## Step 4: Run analysis

### Pre-processing

[you can remove this section if no pre-processing is required]

```{r}
```

### Descriptive statistics

```{r}
```

### Inferential statistics

```{r}
```

## Step 5: Conclusion

```{r}
```

[Please also include a brief text summary describing your findings. If this reproducibility check was a failure, you should note any suggestions as to what you think the likely cause(s) might be.]

[This function will output information about the package versions used in this report:]

```{r session_info, include=TRUE, echo=TRUE, results='markup'}
devtools::session_info()
```
