---
title: "COD Reproducibility Report"
output:
  html_document:
    toc: true
    toc_float: true
---

#### Article ID: Xvfpm
#### Pilot: Kyle MacDonald
#### Co-pilot: Tom Hardwicke  
#### Start date: 4/27/17
#### End date: [Insert end date - use US format]   

-------

#### Methods summary: 

> E1 examined whether the acquired memory is different depending on whether exactly the same object layout is either learned in vista or in environmental space. We predicted that knowledge acquired from environmental space preserves features of the spatio- temporal learning process, resulting in higher latency when point- ing to targets with increasing corridor distance, and recall in the order objects were encountered in. We expected recall latency and order of vista space memory to be influenced by the layout structure instead.

> Performance in visual pointing and object placement was ascer- tained after learning an object layout either in an environmental space (ES) or in a vista space (VS).

------

#### Target outcomes: 

For this article you should focus on the findings reported in section 2.2.1. Specifically, you should attempt to reproduce all descriptive and inferential analyses reported in the text below and associated tables/figures:

> Starting with the dimension of corridor distance and its influence on pointing latency, we conducted an ANOVA with the between-participant factor environment (ES vs. VS) and the within-participant factor corridor distance. A main effect of corridor distance, F(3, 66) = 5.47, p = 0.008, ηp2 = 0.20, and an interaction of corridor distance × environment, F(3, 66) = 4.58, p = 0.017, ηp2 = 0.17, but no main effect of environment, F < 1, p > 0.800, were found. Thus, the influence of corridor distance on latency differed between environments. To further examine this interaction we regressed pointing latency onto corridor distance separately for each participant. From these regressions b was extracted. This standardized slope describes the linear change of latency with increasing corridor distance for every participant. Fig. 3, top left, depicts the individual and mean slopes for the two environmental conditions. T-tests were used to analyze slopes. As expected, slopes derived from ES did exceed 0, mean b = 0.22, t(11) = 8.15, p < 0.001, d = 2.35 (see Fig. 3, top right), indicating an increase in pointing latency the more corridors are residing between current and target location. With each additional corridor pointing took on average 1.02 s (SD = 0.53) longer. In VS, which worked as the control condition where no latency increase with ascending corridor distance was expected, the mean slope did not differ from 0, mean b = 0.02, t(11) = 0.63, p = 0.542, d = 0.18. Thus, pointing did not take longer the further away targets were located with respect to corridors. Additionally, a comparison of mean slopes between ES and VS revealed that the linear increase of latency across ascending corridor distance was higher for ES compared to VS, t(22) = −4.28, p < 0.001, ds = 1.75. This pattern was also evident in individual slopes. Whereas in ES data of each single participant rendered a positive slope, in VS this was only the case for 7 out of 12 participants. Results suggest that in ES memory, the spatio-temporal pattern of learning was preserved and this was not due to the structure of the layout itself.

------

```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, warning=FALSE, message=FALSE)
```

## Step 1: Load packages

```{r}
library(tidyverse) # for data munging
library(knitr) # for kable table formating
library(haven) # import and export 'SPSS', 'Stata' and 'SAS' Files
library(readxl) # import excel files
library(CODreports) # custom report functions
library(magrittr)
library(stringr)
```

## Step 2: Load data

```{r}
d <- read_csv("data/data1.csv")
d2 <- read_csv("data/data2.csv")
```

### Data checks

Do we have 26 participants?

```{r}
n_expect <- 26

d %>% 
  select(subjCode) %>% 
  unique() %>% 
  nrow() == n_expect
```


## Step 3: Tidy data

Extract the environment condition, position condition, and presendation condition information from the `environmentCondition_VS_1to4_ES_5` variable. From the codebook, 

> 1: VS, static position, object presentation simultaneous
2: VS, static position, object presentation successively
3: VS, movement, object presentation simultaneous
4: VS, movement, object presentation successively
5: ES, movement, object presentation successively

```{r}
d.tidy <- d %>% 
  mutate(env_cond = ifelse(environmentCondition_VS_1to4_ES_5 %in% c(1:4), "VS", "ES"),
         pos_cond = ifelse(environmentCondition_VS_1to4_ES_5 %in% c(1:2), "static", "movement"),
         present_cond = ifelse(environmentCondition_VS_1to4_ES_5 %in% c(1,3), 
                               "simultaneous", "successive"))
```

Convert numeric `Gender_Male_1_Female_2` variable to factor with meaningful label. From the codebook,

> 1: male; 2: female


```{r}
d.tidy %<>% mutate(gender = ifelse(Gender_Male_1_Female_2 == 1, "male", "female"))
```




## Step 4: Run analysis

### Pre-processing

Exclude participants. From the paper, 

> Two participants had to be excluded. One participant did not perform significantly better than chance level (90) in the pointing task. The other participant had to be excluded due to a lack of comprehension of task instructions. The remaining sample of 24 participants (12 for each condition) had a mean age of M = 26.09 (SD = 6.94, [19;52]) and included twelve females (seven randomly assigned to ES condition, five to VS condition). 

```{r}
```

Exclude trials. From the paper, 

> From the 24 participants approximately 4% of the pointing per- formance data was deleted due to deviation of more than two SD from a participant’s overall mean. 

```{r}

```

Correct for nonsphercity. From the paper, 

> All tests conducted were cor- rected for nonsphericity or inequality of variance when appropri- ate.


### Descriptive statistics

```{r}
```

### Inferential statistics

```{r}
```

## Step 5: Conclusion

```{r}
```

[Please also include a brief text summary describing your findings. If this reproducibility check was a failure, you should note any suggestions as to what you think the likely cause(s) might be.]

[This function will output information about the package versions used in this report:]

```{r session_info, include=TRUE, echo=TRUE, results='markup'}
devtools::session_info()
```
